Model LF

### 2022-10-15 max_dp endogen stød.Rmd
Commit

@@

@@

plot(((emp_05 - emp_bs56)/ emp_bs56), col= "blue", xlab= "Year", ylab= "% Change in UR", main= "UR");
lines(((emp_04 - emp_bs4)/ emp_bs4), col= "black");
legend("left", legend=c("All channels","Insurance rate channel", "Productivity channel", "Wage channel", "Demand channel"),
       lty=c(1),lwd=c(2),bty="n", col = c("blue","black","red"));
grid()
```

@@

```{r}
shock_max_dp_model_shock=shock_max_dp_model %>% window(start= c(2006,3))
```

@@

@@

```{r}
plot(((emp_07 - emp_bs7)*1000), col= "blue", xlab= "Year", ylab= "% Change in employment", main= "Employment", ylim= c(-350, 300));
lines(((emp_04 - emp_bs4)*1000), col= "black");
lines(((emp_02 - emp_bs2)*1000), col= "red");
lines(((emp_01 - emp_00)*1000), col= "green");
legend("left", legend=c("All channels except productivity", "insurance rate channel", "wage channel", "demand channel"),
       lty=c(1),lwd=c(2),bty="n", col = c("blue","black","red", "green"));
grid()
```

>>>>

```{r}
plot(((max_dp_01 - max_dp_00) / max_dp_00), col= "black", xlab= "Year", ylab= "% Change in maximum level of income insurance", main= "Maximum level of incom insurance");
grid()
```

@@

## Scenario 1b max

```{r}
# Define add-factor list (defining shock)
constantAdjList1b <- list(

shock_max_dp_model = TIMESERIES(shock_max_dp_model_shock+1 ,START=c(2006,3),  FREQ='Q')

```{r}
# Simulate the model (following shock)
Shock_1b <- SIMULATE(S_model
                    ,simType='DYNAMIC'
                    ,TSRANGE=c(2006,3,2020,1)
                    ,simConvergence=0.00001
                    ,simIterLimit=100
                    ,ConstantAdjustment=constantAdjList1b
                    )
```

```{r}
###Gengivelse af stød til model
max_dp_01b = Shock_1b$simulation$max_dp
wage_01b = Shock_1b$simulation$wage
komp_r_01b = Shock_1b$simulation$komp_r
part_01b = Shock_1b$simulation$part
yk_ds_01b = Shock_1b$simulation$yk_ds
pc_ds_01b = Shock_1b$simulation$pc_ds
wage_ds_t_01b = Shock_1b$simulation$wage_ds_t
ur_ds_01b = Shock_1b$simulation$ur_ds
emp_01b = Shock_1b$simulation$emp
yd_hk_ds_01b = Shock_1b$simulation$yd_hk_ds

tilpas_pr_01b = Shock_1b$simulation$tilpas_pr
u_ds_01b = Shock_1b$simulation$u_ds
part_01b = Shock_1b$simulation$part
nben_h_01b = Shock_1b$simulation$nben_h
wage_ds_01b = Shock_1b$simulation$wage_ds
dp_person_01b = Shock_1b$simulation$dp_person
kont_h_ratio_01b = Shock_1b$simulation$kont_h_ratio

nl_g_01b = Shock_1b$simulation$nl_g

yd_hk_ds_01b = Shock_1b$simulation$yd_hk_ds
wage_gap1_01b = Shock_1b$simulation$wage_gap1
wage_gap_01b = Shock_1b$simulation$wage_gap
prod_01b = Shock_1b$simulation$prod
```

```{r}
plot(((max_dp_01b - max_dp_00) / max_dp_00), col= "black", xlab= "Year", ylab= "% Change in maximum level of income insurance", main= "Maximum level of incom insurance");
grid()
```

@@

plot(((emp_05 - emp_bs56)*1000), col= "blue", xlab= "Year", ylab= "Change in Employment (people)", main= "Employment");
lines(((emp_03 - emp_bs3)*1000), col= "black");
legend("left", legend=c("All channels","Productivity channel"),
       lty=c(1),lwd=c(2),bty="n", col = c("blue","black"));
grid()
```

@@

@@

## Scenario 6b new shock

```{r}
# Define add-factor list (defining shock)
constantAdjList6b <- list(

  shock_kuld_model = TIMESERIES(shock_kuld_model_shock+1 ,START=c(2006,3),  FREQ='Q'),
  shock_max_dp_model = TIMESERIES(shock_max_dp_model_shock+1 ,START=c(2006,3),  FREQ='Q'),
 shock_wage_ds_model = TIMESERIES(shock_wage_ds_model_shock+1 ,START=c(2006,3),  FREQ='Q')

```{r}
# Simulate the model (following shock)
Shock_6b <- SIMULATE(S_model
                    ,simType='DYNAMIC'
                    ,TSRANGE=c(2006,3,2020,1)
                    ,simConvergence=0.00001
                    ,simIterLimit=100
                    ,ConstantAdjustment=constantAdjList6b
                    )
```

yk_ds_06b = Shock_6b$simulation$yk_ds
emp_06b = Shock_6b$simulation$emp
wage_ds_06b = Shock_6b$simulation$wage_ds
ur_ds_06b = Shock_6b$simulation$ur_ds
pc_ds_06b = Shock_6b$simulation$pc_ds
yd_hk_ds_06b = Shock_6b$simulation$yd_hk_ds
pconk_ds_06b = Shock_6b$simulation$pconk_ds
komp_r_06b = Shock_6b$simulation$komp_r
max_dp_06b = Shock_6b$simulation$max_dp
nben_h_06b = Shock_6b$simulation$nben_h
yd_hk_ds_06b = Shock_6b$simulation$yd_hk_ds
ik_06b = Shock_6b$simulation$ik
wage_ds_t_06b = Shock_6b$simulation$wage_ds_t
nben_h_un_06b = Shock_6b$simulation$nben_h_un
nl_g_06b = Shock_6b$simulation$nl_g
nsben_h_06b = Shock_6b$simulation$nsben_h

dp_person_06b = Shock_6b$simulation$dp_person
prod_06bb = Shock_6b$simulation$prod

@@

```{r}
plot(((emp_07 - emp_bs7)*1000), col= "blue", xlab= "Year", ylab= "Change in employment (people)", main= "Change in Employment", ylim= c(-350, 300));
lines(((emp_04 - emp_bs4)*1000), col= "black");
lines(((emp_02 - emp_bs2)*1000), col= "red");
lines(((emp_01 - emp_00)*1000), col= "green");
legend("left", legend=c("All channels except productivity", "insurance rate channel", "wage channel", "demand channel"),
       lty=c(1),lwd=c(2),bty="n", col = c("blue","black","red", "green"));
grid()
```

```{r}
plot(((nl_g_07 - nl_g_bs7)), col= "blue", xlab= "Year", ylab= "Change in Government net lending", main= "Change in Government net-lending");
lines(((nl_g_04 - nl_g_bs4)), col= "black");
lines(((nl_g_02 - nl_g_bs2)), col= "red");
lines(((nl_g_01 - nl_g_00)), col= "green");
legend("left", legend=c("All channels except productivity", "insurance rate channel", "wage channel", "demand channel"),
       lty=c(1),lwd=c(2),bty="n", col = c("blue","black","red", "green"));
grid()
```

```{r}
plot(((yk_ds_05 - yk_ds_bs56) / yk_ds_bs56), col= "blue", xlab= "Year", ylab= "% Change in Gdp", main= "Gdp", ylim= c(-0.0001, 0.0015));
lines(((yk_ds_04 - yk_ds_bs4) / yk_ds_bs4), col= "yellow");
lines(((yk_ds_07 - yk_ds_bs7) / yk_ds_bs7), col= "red");
lines(((yk_ds_03 - yk_ds_bs3) / yk_ds_bs3), col= "black");
lines(((yk_ds_02 - yk_ds_bs2) / yk_ds_bs2), col= "orange");
lines(((yk_ds_01 - yk_ds_00) / yk_ds_00), col= "green");
legend("left", legend=c("All channels","All channels but productivity","Insurance rate channel", "Productivity channel", "Wage channel", "Demand channel"),
       lty=c(1),lwd=c(2),bty="n", col = c("blue", "yellow","red", "black","orange", "green"));
grid()
```

```{r}
plot(((emp_06 - emp_bs56)*1000), col= "blue", xlab= "Year", ylab= "Change in employment (people)", main= "Change in Employment");
lines(((emp_05 - emp_bs56)*1000), col= "black");
legend("left", legend=c("All channels except productivity", "All channels except productivity"),
       lty=c(1),lwd=c(2),bty="n", col = c("blue","black"));
grid()
```

```{r}
plot(((emp_06 - emp_bs56)*1000), col= "blue", xlab= "Year", ylab= "Change in employment (people)", main= "Change in Employment");
lines(((emp_05 - emp_bs56)*1000), col= "black");
legend("left", legend=c("All channels max_dp", "All channels Regul"),
       lty=c(1),lwd=c(2),bty="n", col = c("blue","black"));
grid()
```

```{r}
plot(((emp_06b - emp_bs7)*1000), col= "blue", xlab= "Year", ylab= "Change in employment (people)", main= "Change in Employment");
lines(((emp_07 - emp_bs7)*1000), col= "black");
legend("left", legend=c("All channels except productivity", "All channels except productivity"),
       lty=c(1),lwd=c(2),bty="n", col = c("blue","black"));
grid()
```
